\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-17 tex/figuressupp.tex
update supplemental figure captions

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.6\columnwidth]{fig/apstab3x3.pdf}
\caption{{\bf System stability as a function of connectivity.} The red points represent the average of system stability at each connectivity.}
\label{fig:apstab3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.6\columnwidth]{fig/cycle3x3.pdf}
\caption{{\bf dynamical robustness as a function of number of cycles.} }
\label{fig:cycle3x3}
\end{figure}

>>>>

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.6\columnwidth]{fig/apstab3x3.pdf}
\caption{{\bf System stability as a function of connectivity.} The probability of stability is plotted versus connectivity for all three component systems. We note that, in contrast to robustness, the stability ranges over less than 10\% of the possible dynamic range and demonstrates no obvious significant correlation with connectivity. The red points represent the average of system stability at each connectivity.}
\label{fig:apstab3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.6\columnwidth]{fig/cycle3x3.pdf}
\caption{{\bf Dynamical robustness as a function of cycle number.} Note that number of cycles alone does not classify networks according to their dynamical robustness.}
\label{fig:cycle3x3}
\end{figure}
